Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-10-07 README.Rmd
updated to do list

- Final clean up and proof read of sections 4 and 5
- Prepare for submission (make sure to update date on cover letter)
- Upload the files for submission and submit

>>>>

- Prepare for submission (make sure to update date on cover letter)
- Upload the files for submission and submit
- Save a "snapshot" of the repo in the CyBox folder
